\section{Chatbot design}
\subsection{ Introduction of eCommerce chatbot}

\noindent A chatbot is a computer program that stimulates an interaction or a conversation with customers automatically. These conversations occur based on a set of predefined conditions, triggers and/or events around an online shopper’s buying journey. Chatbots are already being put to use across various business, specially exommerce business, with more consumers finding value in the quick, efficient, and around-the-clock responses chatbots can offer. \\

\noindent With chatbot being integrated in our website, customers online shopping experience is being increased by many reasons:
\begin{itemize}
    \item Customer frequently wants to talk to brands before purchase product to ensure the product meets their needs well or to find out if there is a better option. A chatbot can assist them in making decision, addressing their demand and showing brands care.
    \item Instant responses are always a good strategy to keep consumers. So that, a chatbot with 24/7 availability could assist customers anytime, even at noon or at midnight.
    \item Chatbot is more important in cases an world wide business, when it comes to serving your customers from anywhere in the world, use any languages.
    \item Chatbot helps keep budgets streamlined to focused on marketing and advertising. Although "human" talks are still relevant, there is no need hire too much live agents to tackle customer inquiries.
\end{itemize}

Being aware of the importance and innovative potential of chatbots in running ecommerce businesses, we want to give it a try at BKTechStore, we believe that integrating chatbot technology into our business will provide us with a competitive edge.

\subsection{Technologies}
